### 2017-01-23 section/3_redundancy.tex
address linhai comments
fix some small issues

After identifying \textit{inputs} using static analysis, 
\Tool instruments the program to record \textit{inputs} values at run time.
%Specifically, we will assign
%a unique ID for each source instruction, and a pair of $<InstID, Value>$
%will be recorded at run time with the execution of a source instruction.
The run-time trace also includes information that
differentiate values recorded from different instructions, loop
iterations, loop instances, etc.
%TODO
%All values defined outside the loop is recorded in block O. 
%We record a delimiter, loop instance number and values defined in previous iterations in block H1'.
%Since we only consider redundant iterations from the same loop instance,  
%we do not record values defined outside the loop for cross-iteration redundancy. 
Once the trace under problematic workload is collected either during
off-line debugging or production runs, 
\Tool will process the trace and decide
whether the loops under study contain cross-iteration or 
cross-loop redundancy. 
%We will first present our high-level algorithms, followed
%by the exact implementation.

\paragraph{High-level algorithms}
We need to answer two questions:
how to judge whether
two iterations or loop-instances are doing redundant work, and
how to judge whether a loop contains sufficient redundant
computation to be inefficient.
Our answer stick to one principle: there should be
sufficient amount of redundant computation to make a loop likely culprit
for a user-perceived performance problem and to make itself worthwhile to
get optimized by developers.

@@

Checking cross-loop redundancy goes through several
steps. First, for $k$ dynamic instances of a static loop $L$ that appear
at run time, denoted as $l_1$, $l_2$,
..., $l_k$, we check whether redundancy exists between $l_1$ and $l_2$, 
$l_2$ and $l_3$, and so on. Second, we compute a 
\textit{cross-loop redundancy rate} for $L$:
Rate$_\text{C.L.}$ = $\frac{\text{\# of redundant pairs}}{\text{\# of pairs}}$
(In this example, $\text{\# of pairs}$ is $k-1$).
This rate ranges between 0 and 1, the smaller it is the less redundancy
$L$ contains.
We only check redundancy between consecutive loop instances, because  
checking that between every pairs of loop
instances is time consuming.

@@

We calculate the redundancy for one input instruction $I$ by normalizing the
edit-distance between the two sequences of values returned by $I$ in the two
loop instances, denoted by $SeqA$ and $SeqB$. 
The exact formula is the following:

%\[
%\Scale[0.8]{
%min\_dist(SeqA, SeqB) = min(dist(SeqA,SeqB), r\_dist(SeqA, SeqB))
%}
%\]

\vspace{-0.1in}
\[
\Scale[0.8]{
	Redundancy(I) =  \frac{EditDistance(SeqA, SeqB) - |Length(SeqA) - Length(SeqB)|}{max(Length(SeqA), Length(SeqB))}
}
\]

@@

For cross-loop redundancy analysis,
We randomly decide at the beginning
of every loop instance whether to track values for this instance. 
Since we will need to compare two consecutive loop
instances for redundancy, once we decide to sample one loop instance, we will
make sure to sample the immediate next loop instance too.
The implementation is straightforward by cloning the whole loop and making
sampling decisions in the loop pre-headers.
%; (2)
%sampling is conducted when \texttt{CurrentID} equals either
%\texttt{NextSampleID} or \texttt{NextSampleID}$+1$, with \texttt{NextSampleID}
%increased by a random value in the latter case.

@@

\Tool suggests a fix strategy for each inefficient loop 
and provides related information for carrying out that strategy.
This process is straightforward following our taxonomy discussion in 
Section \ref{sec:study}, as there is often only one or two natural fix 
strategies for each sub-category of root causes.

>>>>

After identifying \textit{inputs} using static analysis, 
\Tool instruments the program to record \textit{input} values at run time.
%Specifically, we will assign
%a unique ID for each source instruction, and a pair of $<InstID, Value>$
%will be recorded at run time with the execution of a source instruction.
The run-time trace also includes information that
differentiate values recorded from different instructions, loop
iterations, loop instances, etc.
%TODO
%All values defined outside the loop is recorded in block O. 
%We record a delimiter, loop instance number and values defined in previous iterations in block H1'.
%Since we only consider redundant iterations from the same loop instance,  
%we do not record values defined outside the loop for cross-iteration redundancy. 
Once the trace under problematic workload is collected either during
off-line debugging or production runs, 
\Tool will process the trace and decide
whether the loops under study contain cross-iteration or 
cross-loop redundancy. 
%We will first present our high-level algorithms, followed
%by the exact implementation.

\paragraph{High-level algorithms}
We need to answer two questions:
how to judge whether
two iterations or loop-instances are doing redundant work, and
how to judge whether a loop contains sufficient redundant
computation to be inefficient.
Our answer sticks to one principle: there should be
sufficient amount of redundant computation to make a loop likely culprit
for a user-perceived performance problem and to make itself worthwhile to
get optimized by developers.

@@

Checking cross-loop redundancy goes through several
steps. First, for $k$ dynamic instances of a static loop $L$ that appear
at run time, denoted as $l_1$, $l_2$,
..., $l_k$, we check whether redundancy exists between $l_1$ and $l_2$, 
$l_2$ and $l_3$, and so on. Second, we compute a 
\textit{cross-loop redundancy rate} for $L$:
Rate$_\text{C.L.}$ = $\frac{\text{\# of redundant pairs}}{\text{\# of pairs}}$
(In this example, $\text{\# of pairs}$ is $k-1$).
This rate ranges between 0 and 1, the smaller it is the less redundancy
$L$ contains.
%We only check redundancy between consecutive loop instances, because  
%checking that between every pairs of loop
%instances is time consuming.
{\color{red} We only check redundancy between consecutive loop instances.
This could bring false negatives, but checking redundancy between every pairs of loop instances is time consuming.}

@@

{\color{red} We calculate the redundancy for one input instruction $I$ by using 1 to subtract the normalized
edit-distance between the two sequences of values returned by $I$ in the two
loop instances, denoted by $SeqA$ and $SeqB$. 
The exact formula is the following:
}
%\[
%\Scale[0.8]{
%min\_dist(SeqA, SeqB) = min(dist(SeqA,SeqB), r\_dist(SeqA, SeqB))
%}
%\]

\vspace{-0.1in}
\[
\Scale[0.8]{
	Redundancy(I) = 1 - \frac{EditDistance(SeqA, SeqB) - |Length(SeqA) - Length(SeqB)|}{min(Length(SeqA), Length(SeqB))}
}
\]

@@

For cross-loop redundancy analysis,
we randomly decide at the beginning
of every loop instance whether to track values for this instance. 
Since we will need to compare two consecutive loop
instances for redundancy, once we decide to sample one loop instance, we will
make sure to sample the immediate next loop instance too.
The implementation is straightforward by cloning the whole loop and making
sampling decisions in the loop pre-headers.
%; (2)
%sampling is conducted when \texttt{CurrentID} equals either
%\texttt{NextSampleID} or \texttt{NextSampleID}$+1$, with \texttt{NextSampleID}
%increased by a random value in the latter case.

@@

\Tool suggests a fix strategy for each inefficient loop 
and provides related information for carrying out that strategy.
This process is straightforward following our taxonomy discussion in 
Section \ref{sec:study}, as there are often only one or two natural fix 
strategies for each sub-category of root causes.
